### 2014-11-12 ThesisJo/derivations.tex
la2pdf commit - 2014:11:12	19:03:21	(Wed12.Nov)

>>>>

\section{Solution}

Instead of solving the wave equation directly, we will make a qualified guess that the solution takes the form of a complex exponential:
%
\begin{align}
s(\p,t) &= A\,e^{j(\omega t - \k\dot\p)}
\end{align}
%

\section{Absorption}

Our derivation of the wave equation assumed no loss of energy. In practice the wave's energy is abosorbed through viscous losses, heat conduction losses and intermolecular losses. These are strongly dependent on frequency. The wave equation can be adapted to account for absorption by assuming a complex sound speed, which will lead to a solution to the wave equation with a real exponential term. In this thesis we will not concern ourselves
